---
title: "Creating the Submission"
author: "Martin Dobiasch"
date: "05. Oktober 2015"
output: html_document
---

This ''document'' is how I came up with my solution.

The first step. Read data and explore it

```{r,cache=TRUE, eval=FALSE}
test<- read.csv("UCI HAR Dataset/test/X_test.txt")
summary(test)
```
Shows only a bunch of columns but nothing easily comprehendable.
However, taking a closer look reveals that the separator is not set to the correct value (space). 

```{r,cache=TRUE, eval=FALSE}
test<- read.csv("UCI HAR Dataset/test/X_test.txt",sep=" ")
head(test)
```
Outputs a table with 4311 rows and 667 columns. Still not good. 
Especially, since when reading ''features_info.txt'' and ''features.txt'' reveals that there should be 561 columns.
Running: 
```{r engine='bash', eval=FALSE}
head -n 1 UCI\ HAR\ Dataset/test/X_test.txt | wc
```
underpins this aswell. 

```{r, eval=FALSE}
head(test,n=1)
```
shows there are a lot of `NA`s in the data which are not supposed to be there. 
Well googling for this problem quickly reveals I am using ''the wrong function''

```{r,cache=TRUE}
test<- read.table("UCI HAR Dataset/test/X_test.txt")
head(test,n=1)
```

Next step as I want to have super modular code is to read the column description into R:
```{r, cache=TRUE}
features= read.table("UCI HAR Dataset/features.txt",colClasses = c("numeric","character"))
```

Now its time to create a code that merges the data. Additionally, the columns are named using the `features` data:
```{r,cache=TRUE,eval=FALSE}
test<- read.table("UCI HAR Dataset/test/X_test.txt")
train<- read.table("UCI HAR Dataset/train/X_train.txt")
data<- rbind(test,train)
colnames(data)<-features$V2
```

Executing
```{r, eval=FALSE}
# Remove the old data
rm(test)
rm(train)
```     
would result in an empty `data` variable as all connected data would have been removed!

When now fiddeling around for selecting the data using ``select(data, matches("(mean|std)"))`` it turns out there is an error ``Error: found duplicated column name``. The cause for this error are of course the column names. Thus using a workaround for the colnames the select statement can be used. 
http://stackoverflow.com/questions/28549045/dplyr-select-error-found-duplicated-column-name

```{r,cache=TRUE,eval=FALSE}
# Workaround
valid_column_names <- make.names(names=features$V2, unique=TRUE, allow_ = TRUE)

#Read the data
test<- read.table("UCI HAR Dataset/test/X_test.txt")
train<- read.table("UCI HAR Dataset/train/X_train.txt")

#Combine the data
data<- rbind(test,train)
colnames(data)<- valid_column_names

#Select the data
data_selected<-select(data, matches("(\\.mean\\.|\\.std\\.)"))
```

The above gives a first shot. However it is missing the subject and activity classification needed for step 5.

```{r,cache=TRUE}
require(dplyr)

# Workaround
valid_column_names <- make.names(names=features$V2, unique=TRUE, allow_ = TRUE)

#Read the data
sub<- read.table("UCI HAR Dataset/test/subject_test.txt")
class<- read.table("UCI HAR Dataset/test/y_test.txt")
test<- read.table("UCI HAR Dataset/test/X_test.txt")
test<- cbind(sub,class,test)

train<- read.table("UCI HAR Dataset/train/X_train.txt")
sub<- read.table("UCI HAR Dataset/train/subject_train.txt")
class<- read.table("UCI HAR Dataset/train/y_train.txt")
train<- cbind(sub,class,train)

#Combine the data
data<- rbind(test,train)
colnames(data)<- c("subject", "activity", valid_column_names)

#Select the data
data_selected<-select(data, matches("(subject|activity|\\.mean\\.|\\.std\\.)"))
```

Next is step 5. It should be possible to summarise the data using the `summary` function. No thats not the function it is prob. `summarise`. 
As it turns out this is the right function. 
However, there is still something needed: As there are a lot of columns it would be tedious to write a summary-statement for each of them.
The solution to this is to use the `summarise_each` function.

```{r, cache=TRUE}
result<- data_selected %>% group_by(subject,activity) %>% summarise_each(funs(mean))

head(result)
```

Et voila. Now the only thing which is missing is to create the final submission and create neater variable names. 

